---
# title: "pokerena"
output: github_document
---

# Pokerena `r emo::ji("club_suit")` `r emo::ji("diamond_suit")` `r emo::ji("heart_suit")` `r emo::ji("spade_suit")`

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = T, warning = F, error = F, message = F, fig.path = "man/figures/")
```

A Poker engine for AI development in R. 

```{r, echo = F}
# devtools::install_github("hadley/emo")
pacman::p_load(tidyverse, devtools, crayon)
load_all()

# keywords <- emo::ji_keyword
# keywords[stringr::str_detect(names(keywords), "suit")]
```


## Tutorial

This tutorial leads you to start point of poker AI development...

... But first install. 

```{r, eval = F}
devtools::install_github("systats/pokerena")
```


There are two main ways to deploy a bot, as there are two ways for using the poker backend. 

1. preregister functions in interactive R session
2. call a separate HTTP API endpoint from a job. 

In general players just return a tibble with an action and amount of chips to bet. 


```{r}
player_call <- function(state_, ...){
  tibble(chips = state_$to_call, action = "call")
}
```

```{r}
players <- rbind(
  tibble(name = "call", fun = list(player_call)), # player 1
  tibble(name = "radnom1", fun = list(player_random)), # player 2
  tibble(name = "fold", fun = list(player_fold)) # player 4
) %>% mutate(credit = 100, bb = 2)
```

```{r, message=T}
g <- game$new(players, delay = 0)
g$run()
```

```{r}
g$session %>% glimpse
```

```{r}
g$events %>% glimpse
```


Similarily a tournament can be set up.

```{r}
config <- list(
  credit = 100, # inital stack size, if NULL assumes individual credits
  max_round = 50, # how many rounds at max should be played
  bb = 2, # inital big blind
  bb_rounds = 10, # increase blinds after x hands
  bb_slope = "linear" # how to increase blinds
)

tourn <- tournament$new(players, config)
tourn$run()
```


```{r}
tourn$games %>% glimpse
```

```{r}
tourn$games %>% 
  transmute(id = 1:n(), result) %>% 
  unnest("result") %>% 
  distinct(id, bb) %>% 
  ggplot(aes(id, bb)) +
  geom_line()
```


```{r}
tourn$games %>% 
  transmute(id = 1:n(), result) %>% 
  unnest("result") %>% 
  ggplot(aes(id, credit, colour = name)) + 
  geom_line()
```


```{r}
tourn$games %>% 
  transmute(id = 1:n(), result) %>% 
  unnest("result") %>% 
  group_by(id) %>% 
  mutate(winner_name  = ifelse(winner == 1, name, NA)) %>% 
  fill(winner_name, .direction = "updown") %>% 
  ungroup() %>% 
  group_by(name, winner_name) %>% 
  summarise(net = sum(net))
```


## Main Dependencies

* `Poker`: generic R poker hand evaluator
* `Plumber`: serving a local poker server
* `R6`: class management 
* `Tidyvrse`: everything else 

## Unit Testing

```{r}
testthat::test_package("pokerena")
```


## Roadmap

### Engine

- [x] support going allin 
- [x] poker hand evaluation
- [x] multiple split and side pots
- [x] tournament flow
- [ ] log messages for debugging
- [ ] unit tests for more situations
- [ ] improved cli output


### AI

- [ ] RL script with replay buffer
- [ ] support for multiplayer self-play
- [ ] support replay for MCCFR
- [ ] tree search and pruning


### Analytics

- [ ] Leaderboard
- [ ] HUD
